Illustration of Adaptive Shrinkage

### 2016-09-30 analysis/adaptive_shrinkage.Rmd
Made some adjustments to adaptive_shrinkage.Rmd so that it renders correctly in atom.

TO DO: explain what this chunk does.

```{r chunk-options,include = FALSE}
source("chunk-options.R")
```

We simulate from two scenarios, the first with effects more peaked
about zero, the second with effects less peaked.

```{r initialize}
set.seed(100)
library(ashr)
library(ggplot2)
library(scales)
source("../code/dsc-shrink/datamakers/datamaker.R")

NSAMP=1000
s = 1/rgamma(NSAMP,5,5)
sim.bignormal = rnormmix_datamaker(args=list(g=normalmix(c(1),c(0),c(4)),
                        min_pi0=0,
                        max_pi0=0,
                        nsamp=NSAMP,
                        betahatsd=s
                      ))

sim.spiky = rnormmix_datamaker(args=list(g=normalmix(c(.4,.2,.2,.2),c(0,0,0,0),c(.25,.5,1,2)),
                        min_pi0=0,
                        max_pi0=0,
                        nsamp=NSAMP,
                        betahatsd=s
                      ))

```

Now run ash on both:
```{r run-ash}
beta.bignormal.ash = ash(sim.bignormal$input$betahat, s)
beta.spiky.ash = ash(sim.spiky$input$betahat, s)
```

@@

```{r plotting}
make_df_for_ashplot = function(sim1,sim2,ash1,ash2,name1="spiky",name2="big-normal"){
  df = data.frame(betahat = c(sim1$input$betahat,sim2$input$betahat),
                beta_est = c(get_pm(ash1), get_pm(ash2)),
                lfsr = c(get_lfsr(ash1), get_lfsr(ash2)),
                s=c(sim1$input$sebetahat,sim2$input$sebetahat),
                scenario=c(rep(name1,NSAMP),rep(name2,NSAMP)))
  df$signif = df$lfsr<0.05
  return(df)
}

@@

```{r}
pval_plot=function(df){
  ggplot(df,aes(x=pnorm(-abs(betahat/s)),y=lfsr,color=log(s))) + geom_point() +  facet_grid(.~scenario) +xlim(c(0, 0.025)) + xlab("p value") + ylab("lfsr") +
  scale_colour_gradient2(midpoint = 0,low="blue", mid="white",high="red")  
}
pval_plot(df)
```

>>>>

First, we load the necessary libraries, and specify settings for
displaying the plots in the rendered document.

```r
library(ashr)
library(ggplot2)
library(scales)
source("chunk-options.R")
```

We simulate from two scenarios: in the first scenario, the effects are more
peaked about zero (**sim.spiky**); in the second scenario, the effects are
less peaked (**sim.bignormal**).

```r
set.seed(100)
source("../code/dsc-shrink/datamakers/datamaker.R")

NSAMP = 1000
s     = 1/rgamma(NSAMP,5,5)

sim.spiky =
  rnormmix_datamaker(args = list(g = normalmix(c(0.4,0.2,0.2,0.2),
                                               c(0,0,0,0),
                                               c(0.25,0.5,1,2)),
                                  min_pi0   = 0,
                                  max_pi0   = 0,
                                  nsamp     = NSAMP,
                                  betahatsd = s))

sim.bignormal =
  rnormmix_datamaker(args = list(g         = normalmix(1,0,4),
                                 min_pi0   = 0,
                                 max_pi0   = 0,
                                 nsamp     = NSAMP,
                                 betahatsd = s))
```

Now we run ash on both data sets.

```r
beta.spiky.ash     = ash(sim.spiky$input$betahat,s)
beta.bignormal.ash = ash(sim.bignormal$input$betahat,s)
```

@@

```r
make_df_for_ashplot = function(sim1,sim2,ash1,ash2,name1="spiky",name2="big-normal"){
  df = data.frame(betahat = c(sim1$input$betahat,sim2$input$betahat),
                beta_est = c(get_pm(ash1), get_pm(ash2)),
                lfsr = c(get_lfsr(ash1), get_lfsr(ash2)),
                s=c(sim1$input$sebetahat,sim2$input$sebetahat),
                scenario=c(rep(name1,NSAMP),rep(name2,NSAMP)))
  df$signif = df$lfsr<0.05
  return(df)
}

@@

```r
pval_plot=function(df){
  ggplot(df,aes(x=pnorm(-abs(betahat/s)),y=lfsr,color=log(s))) + geom_point() +  facet_grid(.~scenario) +xlim(c(0, 0.025)) + xlab("p value") + ylab("lfsr") +
  scale_colour_gradient2(midpoint = 0,low="blue", mid="white",high="red")
}
pval_plot(df)
```
